An Analysis of daily shelter and overnight service usage in Toronto focusing on shelter occupancy and capacity

### 2024-09-27 paper/paper.qmd
Final Revision

---
title: "An Analysis of daily shelter and overnight service usage in Toronto focusing on shelter occupancy and capacity"
author: 
  - "Victoria Zheng"
thanks: "Code and data are available at: https://github.com/Anjojoo/Toronto-Overnight-Servive-Occupancy-Capacity."
date: today
date-format: long
abstract: "This paper analyzes the overnight service occupancy and capacity of shelters in Toronto, utilizing data from OpenDataToronto. Employing the R programming language along with various packages, the analysis focuses on shelter usage trends, specifically examining changes in occupancy rates and actual capacity over the years. The results indicate an overall upward trend in shelter occupancy rates, while a significant decline in actual capacity was observed in 2024. These findings highlight the need for strategic resource allocation and improved response strategies concerning shelter occupancy in the future."
format: 
  pdf: 
    toc: true
    toc-depth: 2
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "An Analysis of daily shelter and overnight service usage in Toronto focusing on shelter occupancy and capacity"
author: 
  - "Angel Xu"
thanks: "Code and data are available at: https://github.com/Anjojoo/Toronto-Overnight-Servive-Occupancy-Capacity."
date: today
date-format: long
abstract: "This paper analyzes the overnight service occupancy and capacity of shelters in Toronto, utilizing data from OpenDataToronto. Employing the R programming language along with various packages, the analysis focuses on shelter usage trends, specifically examining changes in occupancy rates and actual capacity over the years. The results indicate an overall upward trend in shelter occupancy rates, while a significant decline in actual capacity was observed in 2024. These findings highlight the need for strategic resource allocation and improved response strategies concerning shelter occupancy in the future."
format: 
  pdf: 
    toc: true
    toc-depth: 2
number-sections: true
bibliography: references.bib
---
